### 2015-07-23 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Buildbot ran the code beautifier.
Final modifs in Axisem dir: 1

\noindent 2 files produced by meshfem3D (input\_box.txt and input\_box\_sem\_cart.txt) were copied (and the first line indicating the number of line to be read were add at the beginning of the files too) during the STEP 1 in the AxiSEM SOLVER dir.

@@

\noindent ./add\_line\_number\_in\_points\_lists.sh (rename files 'list\_gll\_boundary\_spherical.txt' \& \\ 'list\_gll\_boundary\_cartesian.txt', and add number of lines) \\

\noindent run ./sub\_called\_batch\_for\_AxiSEM\_Curie\_CD.sh (submit the job on Curie)

>>>>

\noindent 2 files produced by meshfem3D ('list\_gll\_boundary\_spherical.txt' and 'list\_gll\_boundary\_cartesian.txt') were copied during the STEP 1 in the AxiSEM SOLVER dir.

@@

\noindent ./add\_line\_number\_in\_points\_lists.sh : rename files 'list\_gll\_boundary\_spherical.txt' and \\ 'list\_gll\_boundary\_cartesian.txt' to 'input\_box.txt' and 'input\_box\_sem\_cart.txt', resp. and add number of lines at the beginning of the two files too. \\

\noindent run ./sub\_called\_batch\_for\_AxiSEM\_Curie\_CD.sh : submit the job on Curie.
